Effects of the body force on the evacuation dynamics

### 2020-01-16 paper.tex
modifique el caption de strain rate
agregue las conclusiones

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./vx_profile.eps}\label{vx_profile}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./strain_rate_vs_kn.eps}\label{strain_rate_vs_kn}}\\
\caption[width=0.47\columnwidth]{(a) Velocity in the $x$ coordinate as a function of the transversal coordinate $y$ for three different stiffness values $k$ (see the label). (b) Strain rate as a function of the stiffness level $k$.  The measurements correspond to a corridor of 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$. The global density was 7 p~m$^{-2}$.  }
\label{profile_strain}
\end{figure}

@@

>>>>

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./vx_profile.eps}\label{vx_profile}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./strain_rate_vs_kn.eps}\label{strain_rate_vs_kn}}\\
\caption[width=0.47\columnwidth]{(a) Velocity in the $x$ coordinate as a function of the transversal coordinate $y$ for three different stiffness values $k$ (see the label). (b) Strain rate as a function of the stiffness level $k_n$ for three different global density values (see label). The measurements correspond to a corridor of 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$. The global density was 7 p~m$^{-2}$.  }
\label{profile_strain}
\end{figure}

@@

In this research, we have explored the effects of the body force in the original SFM. We showed that the stiffness coefficient ($k_n$) has a significant impact on the evacuation dynamics (bottleneck) and also in the dynamics of pedestrians walking along a straight corridor.\\

In the bottleneck geometry, the evacuation time diminishes (pedestrians move faster) as pedestrians become stiffer for all the ranges of the desired velocities explored. This phenomenon happens because increasing the stiffness level promotes the repulsion between pedestrians pair interactions. As pedestrians detach from each other, the friction force diminishes due to the reduction of overlap and contacts among them. The general decrease in frictional force reduces the probability of producing a cluster of pedestrians blocking the exist (blocking cluster), which finally leads to a more efficient evacuation dynamics. \\

In the corridor geometry, the walking speed reduces as pedestrians become stiffer. This is the opposite behavior we obtained in bottleneck geometry. The difference is explained because although increasing stiffness further separates individuals, they can not detach from each other as much as possible due to the lateral walls (these walls are not relevant in the bottleneck geometry). Thus, when the stiffness increases, pedestrians reduce the overlap but increase the number of contacts (degree). In high density scenarios, the stiffness promotes the friction force.  Granular materials can behave like fluid or solids, depending on several conditions. If the stiffness level is low, the entire crowd behaves like a viscous fluid (with a parabolic velocity profile). However, if the stiffness level is high enough, the whole crowd behaves like a solid (with a constant velocity profile which depends on the friction against the walls).\\

Regarding the parameters of the model, we found out that it is possible to reduce the original SFM parameters to three dimensionless parameters. The original parameters interrelate to each other through the dimensionless ones. Many different settings can produce the same dimensionless parameters. Thus, no univocal relations can be established between the individualistic parameters and collective dynamics.\\
